BLAST: Block Applications for Things

### 2022-04-08 demo-eswc22/paper.tex
Update demo-eswc22/paper.tex
Co-authored-by: Thomas Wehr <derwehr@gmail.com>

We conducted an evaluation with nine participants. None of the participants had background knowledge regarding the Web of Things, RDF, or SPARQL. Participants were first asked to solve four tasks using BLAST, these included a simple "Hello World!" program, periodic polling of RSSI data by using a loop, reading data from a connected IoT device, and as a final task, reading data and processing it using logical operators. After the successful completion of these tasks, the participants filled out the SUS questionnaires. The achieved SUS score across all questionnaires is 81.4 out of 100 possible points, which corresponds to good usability.

>>>>

We conducted an evaluation with nine participants. None of the participants had background knowledge regarding the Web of Things, RDF, or SPARQL. Participants were first asked to solve four tasks using BLAST, these included a simple ``Hello World!'' program, periodic polling of RSSI data by using a loop, reading data from a connected IoT device, and as a final task, reading data and processing it using logical operators. After the successful completion of these tasks, the participants filled out the SUS questionnaires. The achieved SUS score across all questionnaires is 81.4 out of 100 possible points, which corresponds to good usability.
